\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}

%====================
% STYLE DEFINITIONS
%====================

% FONT STUFF
\RequirePackage[T1]{fontenc}
\RequirePackage[default,semibold]{sourcesanspro}
\RequirePackage[10pt]{moresize}


% MARGINS & SPACING
\RequirePackage[margin=0.6in, top=0.6in, bottom=0.9in]{geometry}
\raggedright
\raggedbottom

% COLOR
\RequirePackage{xcolor}
\definecolor{highlight}{RGB}{33, 37, 41} % Deep Charcoal



% BULLET POINTS
\RequirePackage[inline]{enumitem}
\setlength{\tabcolsep}{0in}

% SECTION FORMATTING
\RequirePackage[nostruts]{titlesec}
\titlespacing*{\section}{0em}{0.4em}{0.2em}
% Section format: Blue, Small Caps, Large, No Number (empty label), Horizontal Rule
\titleformat{\section}{\color{highlight} \scshape \raggedright \large}{}{0em}{}[\vspace{-0.5em}\hrulefill]

% SUBSECTION FORMATTING
\titlespacing*{\subsection}{0em}{1em}{0.2em}
\titleformat{\subsection}{\bfseries}{}{0em}{}[]

% CUSTOM COMMANDS
\newcommand{\skills}[1]{\textbf{#1}}

% NO PAGE NUMBER
\pagenumbering{gobble}

% LANGUAGE SUPPORT
\RequirePackage[english]{babel}

% LINKS (Moved to end of preamble)
\RequirePackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=highlight}



%====================
% CONTACT INFORMATION
%====================
\def\name{Cem Karakurt}
\def\city{Berlin, Germany}
\def\email{ickarakurt@gmail.com}
\def\LinkedIn{ickarakurt}
\def\github{ickarakurt}
\def\role{Senior Full Stack Engineer}

\begin{document}

%====================
% HEADER (ATS Friendly: In-flow, no fancyhdr)
%====================
\begin{center}
    {\Huge \skills{\name}} \\[0.2cm]
    {\color{highlight} \Large{\role}} \\[0.2cm]
    \city \ $\cdot$ \ \href{mailto:\email}{\email} \ $\cdot$ \ \href{https://cemkarakurt.com}{cemkarakurt.com} \\
    \href{https://github.com/\github}{github.com/\github} \ $\cdot$ \ \href{https://www.linkedin.com/in/\LinkedIn}{linkedin.com/in/\LinkedIn}
\end{center}

\vspace{1em}

%====================
% SUMMARY
%====================
\section{Summary}

Senior Full Stack Engineer with 6+ years building scalable web applications using \textbf{React.js}, \textbf{Node.js}, \textbf{Ruby on Rails}, and \textbf{AWS}. Strong experience across the full stack, from database design and cloud infrastructure to frontend development and testing. Proficient in leveraging AI tools to accelerate development and solve complex problems efficiently.
%====================
% SKILLS
%====================
\section{Skills}

\noindent
\skills{Languages \& Frameworks}: TypeScript, Node.js (Express.js), React.js, Ruby on Rails, PHP, Next.js \\
\skills{Databases}: DynamoDB, PostgreSQL, MySQL, Couchbase, Redis \\
\skills{Cloud \& DevOps}: AWS (Lambda, Kinesis, S3, API Gateway), Terraform, Docker, NGINX, CI/CD pipelines \\
\skills{Frontend Technologies}: React.js, Redux, Tailwind CSS, shadcn/ui, Storybook, WebRTC \\
\skills{Testing}: Playwright, Jest, React Testing Library \\
\skills{Development Practices}: Agile (Scrum, Kanban), Microservices, Microfrontends, Monorepos, RBAC \\
\skills{Communication}: English (fluent), Turkish (native), German (learning)

%====================
% EXPERIENCE
%====================
\section{Experience}

\textbf{Babbel GmbH} \hfill Berlin, Germany \\
\textit{Senior Full Stack Engineer (Promoted April 2024)} \hfill March 2022 --- June 2025
\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep, topsep=2pt]
    \item Built Full Stack features for the live-lesson platform (AWS Lambda, Step Functions, React.js), provisioning required infrastructure via Terraform.
    \item Led the SmartCat localization discovery (shared company-wide) and documented the department's \skills{Microfrontend} architecture.
    \item Improved the Microfrontend deployment system to support multi-version rendering on a single page, enabling independent branch deployments.
    \item Reduced frontend bundle size by 40\% by optimizing third-party dependencies to enable efficient tree-shaking.
    \item Led technical discovery for E2E frameworks (Playwright vs. Cypress) and implemented initial test suites for booking and subscription flows.
    \item Ran agile ceremonies (standups, refinements), handled production on-call support, and focused on continuous refactoring and dependency updates.
\end{itemize}
\textbf{Tech Stack:} Node.js, TypeScript, React.js, Redux Toolkit, AWS (Lambda, EventBridge, DynamoDB), Terraform, Playwright, Storybook, Microfrontends, Vite

\medskip

\textbf{11Sight LLC} \hfill Remote \\
\textit{Software Engineer} \hfill August 2020 --- December 2021
\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep, topsep=2pt]
    \item Implemented a centralized SSO provider using \skills{Doorkeeper} to sync authentication across multiple products, enabling a unified login experience.
    \item Built a reporting system for group meetings by creating custom \skills{Prosody} modules that integrated Jitsi events with Ruby on Rails APIs and dashboards.
    \item Created a feature-management system for organizations to toggle platform services (e.g., recording, transcription) through the main dashboard and Jitsi UI.
    \item Managed \skills{AWS EC2 Auto Scaling} for recording services and handled deployments and server maintenance for Jitsi-based products.
    \item Developed RESTful APIs and background jobs with \skills{Sidekiq}, maintaining test coverage and automated Swagger documentation via \skills{RSpec}.
\end{itemize}
\textbf{Tech Stack:} Ruby on Rails, React.js, PostgreSQL, Jitsi, WebRTC, Prosody (XMPP), OAuth 2.0, Redis, Sidekiq, WebSocket, NGINX, AWS EC2, RSpec

\medskip

\textbf{Countly} \hfill Izmir, Turkey \\
\textit{Software Engineer} \hfill December 2019 --- June 2020
\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep, topsep=2pt]
    \item Built demo SPAs (React.js) and a mobile app (Swift) showcasing analytics features like session tracking, funnels, and user segmentation.
    \item Provided technical support to enterprise customers integrating Countly SDK into their applications.
\end{itemize}
\textbf{Tech Stack:} Node.js, Next.js, i18Next, Tailwind CSS, Swift

\medskip

\textbf{Gatemarine} \hfill Izmir, Turkey \\
\textit{Software Engineer} \hfill May 2019 --- November 2019
\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep, topsep=2pt]
    \item Built real-time tracking platform for Raspberry Pi sensor network with local and centralized dashboards.
    \item Used Couchbase replication to maintain data consistency between edge devices and central server.
    \item Developed an internal inventory management tool using CodeIgniter (PHP) and Bootstrap.
    \item Managed Linux servers, configured NGINX, and handled deployment pipelines.
\end{itemize}
\textbf{Tech Stack:} Node.js, Couchbase, React.js, Redux, NGINX, WebSocket, PHP, MySQL

%====================
% CERTIFICATIONS
%====================
\section{Certifications}

\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep]
  \item AWS Certified Developer – Associate (Amazon Web Services, Issued: April 02, 2024)
\end{itemize}

%====================
% EDUCATION
%====================
\section{Education}

\noindent \skills{Bachelor of Science in Computer Engineering}, \textit{Izmir Institute of Technology} \hfill 2016 --- 2021 \\
\skills{Associate of Science in Business Management}, \textit{Anadolu University} \hfill 2018 --- 2020

\end{document}
