
%====================
% PROJECTS
%====================
\section{Projects}

\textbf{Postgrenext} \hfill \href{https://github.com/ickarakurt/postgrenext}{github.com/ickarakurt/postgrenext} \\
\textit{Open-source real-time PostgreSQL monitoring and performance visualization tool.} \hfill January 2026 --- Present
\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep, topsep=2pt]
    \item Built a real-time monitoring dashboard using Next.js Server Actions and PostgreSQL system catalogs.
    \item Implemented query profiling, performance analysis, and lock monitoring for database optimization.
    \item Created interactive visualizations and data tables using Recharts and TanStack Table for query statistics.
    \item Designed a modern, responsive UI with full dark mode support using shadcn/ui and Tailwind CSS.
\end{itemize}
\textbf{Tech Stack:} Next.js, React.js, TypeScript, PostgreSQL, Tailwind CSS, shadcn/ui, Recharts, TanStack Table

\medskip

\textbf{Travana} \hfill \href{https://travana.com}{travana.com} \\
\textit{Analytics platform providing deep insights and strategy tools for Travian browser game players.} \hfill January 2026 --- Present
\begin{itemize}[leftmargin=1.5em, label=\textbullet, noitemsep, topsep=2pt]
    \item Built a Full Stack application serving player rankings, alliance analytics, and interactive map features.
    \item Designed an optimized PostgreSQL database with monthly partitioning and BRIN indexes for millions of snapshots.
    \item Implemented a robust data pipeline for parsing game data with batch processing and duplicate handling.
    \item Integrated Better Auth, email notifications, and Docker deployment with Dokploy for production-level infrastructure.
\end{itemize}
\textbf{Tech Stack:} Next.js, React.js, TypeScript, PostgreSQL, Kysely ORM, Tailwind CSS, shadcn/ui, Better Auth
